---
title: "Programa de Prevenci칩n y Control del Dengue | 2025"
format: 
  dashboard:
    nav-buttons: [twitter, github, facebook]
theme: custom.scss
---

```{r setup}
library(sf)
mapview::mapviewOptions(default = TRUE,
                        basemaps.color.shuffle = FALSE)
```

# [**Hotspots de la Transmisi칩n de Dengue**]{style="font-size:2pt"}
 
::: panel-tabset


### [**P치nuco**]{style="color:#990000"}

<html>
<head>
```{=html}
<style>
body {
  margin: 0px;
  width: auto; 
  height: auto;
}

.wrapper {
    display: grid;
    grid-gap: 1px;
    grid-template-columns: 225px 225px 225px 410px;
    grid-template-rows: 95px 95px 95px 130px;
    background-color: #772953;
    color: "#772953";
  }

  .box {
    background-color: #772953;
    color: "#772953";
    border-radius: 1px;
    padding: 2px;
    font-size: 100%;
  }

  .a {
    grid-column: 1 / 4;
    grid-row: 1 / 4;
  }
  .b {
    grid-column: 4 ;
    grid-row: 1 / 3;
  }
  .c {
    grid-column: 4 ;
    grid-row: 3 / 5 ;
  }
  .d {
    grid-column: 3;
    grid-row: 4;
  }
  .e {
    grid-column: 2;
    grid-row: 4;
  }
  .f {
    grid-column: 1;
    grid-row: 4;
  }
</style>
```
</head>
<body>
::: wrapper
::: {.box .a}
```{r hotspots_dengue_panuco}
# Step 1. extract the locality ####
loc <- rgeomex::extract_locality(cve_edo = "30", 
                                 locality = "Panuco")

# Step 2. Extract the hotspots ####
hotspots <- hotspotsdata::den_hotspots[loc, ]
mapview::mapview(hotspots,
                 zcol = "intensity_gi",
                 layer.name = "Intensidad",
                 label = FALSE,
                 color = "white",
                 lwd = 0.5, 
                 col.regions =  rcartocolor::carto_pal(n = max(hotspots$intensity_gi), 
                                                       name = "OrYel"))

```
:::

::: {.box .b}
```{r forest_plot_panuco, dpi = 300, fig.height= 5,fig.width = 7,fig.align = "center", out.height='100%', out.width = '100%',fig.show = "hold"}
 
# Logistic Regression
hotspots <- hotspots |>
    dplyr::mutate(DENV_2008_2010 = DENV_2008 + DENV_2009 + DENV_2010) |>
    dplyr::mutate(DENV_2011_2014 = DENV_2011 + DENV_2012 + DENV_2013 + DENV_2014) |>
    dplyr::mutate(DENV_2015_2017 = DENV_2015 +  DENV_2016 + DENV_2017) |>
    dplyr::mutate(DENV_2018_2019 = DENV_2018 +  DENV_2019) |>
    dplyr::mutate(DENV_2020_2022 = DENV_2020 +  DENV_2021 + DENV_2022) |>
    dplyr::mutate(DENV_2023_2024 = DENV_2023 +  DENV_2024) 


# Logistic Regression
glm.fit <- glm(hotspots_gi~DENV_2008_2010 + DENV_2011_2014 +
                   DENV_2015_2017 + DENV_2018_2019 +
                   DENV_2020_2022 + DENV_2023_2024,
               data = hotspots, 
               family = binomial)

result <- parameters::model_parameters(glm.fit, 
                                       exponentiate = FALSE)

plotly::ggplotly(plot(result) +
       ggplot2::theme(axis.text.y = ggplot2::element_text(size = 8),
                       axis.text.x = ggplot2::element_text(size = 8),
                       axis.title = ggplot2::element_text(size = 8),
                      plot.margin = ggplot2::unit(c(0,0,0,0), "cm")) +
        ggplot2::scale_y_discrete(labels = c("2008-2010",
                                             "2011-2014", 
                                             "2015-2017",
                                             "2018-2019",
                                             "2020-2022",
                                             "2023-2024")))
```
:::

::: {.box .c}
```{r power_law_plot_panuco,dpi = 300, warning=FALSE, fig.align = "center", out.width = '100%',out.height='100%',fig.show = "hold"}
# Step 7. make the function por calculate the cumulative ####
funcumsum <- function(x){
    x$cumulative_n <- cumsum(x$n_cases)
    x$perc_cumsum_n <- round((cumsum(x$n_cases)/sum(x$n_cases))*100, digits = 1)
    #x$cumulative_ha <- cumsum(x$ha)
    #x$perc_cumsum_ha <- round((cumsum(x$ha)/sum(x$ha))*100, digits = 1)
    x$id <- 1
    x$id_cumsum <- cumsum(x$id)
    x$id_perc_cum <- round((cumsum(x$id)/nrow(x))*100, digits = 1)
    x
}
# step 8.
data_pareto <- hotspots   |>
    # sf::st_drop_geometry()  |>
    # dplyr::mutate(n_cases = rowSums(dplyr::select(., dplyr::starts_with("DENV"))),
    #              loc = "locality")
    #dplyr::mutate(n_cases = rowSums(dplyr::across(DENV_2008:DENV_2021)),
    #              loc = "locality")  |>
    dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    
    dplyr::select(loc, n_cases, hotspots_gi)  |>
    dplyr::arrange(loc, desc(hotspots_gi), desc(n_cases))  |>
    dplyr::group_by(loc)  |>
    tidyr::nest()  |>
    dplyr::mutate(pareto_cases = purrr::map(data,
                                            funcumsum))  |>
    dplyr::select(-data)  |>
    tidyr::unnest(cols = c(pareto_cases))

# step 4. visualization of pareto rules 
plotly::ggplotly(denhotspots::power_law_plot(x = data_pareto) +
                  ggplot2::theme(axis.text.y = ggplot2::element_text(size = 8),
                                 axis.text.x = ggplot2::element_text(size = 8),
                       axis.title = ggplot2::element_text(size = 8),
                      plot.margin = ggplot2::unit(c(0,0,0,0), "cm")))  |> 
  plotly::layout(showlegend = FALSE)






```
:::

::: {.box .d}
```{r gauge_blocks_panuco,fig.align = "center", out.height='90%', out.width = '90%'}
y_hot <- hotspots |> dplyr::filter(hotspots_gi == 1)
centroid <- rgeomex::blocks_ine20_mx_centroid |>
  sf::st_as_sf(coords = c("x", "y"), crs = 4326)
b_loc <- centroid[hotspots, ]
b_hot <- b_loc[y_hot, ]
flexdashboard::gauge(round((nrow(b_hot)/nrow(b_loc))*100, digits = 1),
                     min = 0, max = 100, 
                     symbol = '%', 
                     label = "Manzanas",
                     flexdashboard::gaugeSectors(success = c(0, 30), 
                                                 warning = c(31, 50), 
                                                 danger = c(51, 100),
                                                 colors = c("#11BB33", #"#63C1A0", 
                                                            "#FC8427",
                                                            "#E01A59")))
```
:::

::: {.box .e}
```{r gauge_AGEB_panuco, fig.align = "center", out.height='90%', out.width = '90%'}

y <- hotspots  |>
    sf::st_drop_geometry() |>
     dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    dplyr::select(loc, n_cases, hotspots_gi) 
y_hot <- y |>dplyr::filter(hotspots_gi == 1)
  
flexdashboard::gauge(round((nrow(y_hot)/nrow(y))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "AGEBs",
      flexdashboard::gaugeSectors(success = c(0, 30), 
                                  warning = c(31, 50), 
                                  danger = c(51, 100),
                                  colors = c("#11BB33",
                                             "#FC8427",
                                             "#E01A59")))
```
:::

::: {.box .f}
```{r gauge_casos_panuco, out.height='90%', out.width = '90%', fig.align = "center"}

y <- hotspots  |>
    sf::st_drop_geometry() |>
      dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    dplyr::select(loc, n_cases, hotspots_gi) 
y_hot <- y |>dplyr::filter(hotspots_gi == 1)

flexdashboard::gauge(round((sum(y_hot$n_cases)/sum(y$n_cases))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "Casos de Dengue",
      flexdashboard::gaugeSectors(success = c(11, 100), 
                                  warning = c(6, 10), 
                                  danger = c(0, 5),
                                  colors = c("#11BB33", 
                                             "#FC8427",
                                             "#E01A59")))
```
:::
:::
</body>
</html>


### [**Tuxpan**]{style="color:#990000"}

<html>
<head>

</head>
<body>
::: wrapper
::: {.box .a}
```{r hotspots_dengue_tuxpan}
# Step 1. extract the locality ####
loc <- rgeomex::extract_locality(cve_edo = "30", 
                                 locality = "Tuxpan de Rodriguez Cano")

# Step 2. Extract the hotspots ####
hotspots <- hotspotsdata::den_hotspots[loc, ]
mapview::mapview(hotspots,
                 zcol = "intensity_gi",
                 layer.name = "Intensidad",
                 label = FALSE,
                 color = "white",
                 lwd = 0.5, 
                 col.regions =  rcartocolor::carto_pal(n = max(hotspots$intensity_gi), 
                                                       name = "OrYel"))

```
:::

::: {.box .b}
```{r forest_plot_tuxpan, dpi = 300, fig.height= 5,fig.width = 7,fig.align = "center", out.height='100%', out.width = '100%',fig.show = "hold"}
 
# Logistic Regression
hotspots <- hotspots |>
    dplyr::mutate(DENV_2008_2010 = DENV_2008 + DENV_2009 + DENV_2010) |>
    dplyr::mutate(DENV_2011_2014 = DENV_2011 + DENV_2012 + DENV_2013 + DENV_2014) |>
    dplyr::mutate(DENV_2015_2017 = DENV_2015 +  DENV_2016 + DENV_2017) |>
    dplyr::mutate(DENV_2018_2019 = DENV_2018 +  DENV_2019) |>
    dplyr::mutate(DENV_2020_2022 = DENV_2020 +  DENV_2021 + DENV_2022) |>
    dplyr::mutate(DENV_2023_2024 = DENV_2023 +  DENV_2024) 


# Logistic Regression
glm.fit <- glm(hotspots_gi~DENV_2008_2010 + DENV_2011_2014 +
                   DENV_2015_2017 + DENV_2018_2019 +
                   DENV_2020_2022 + DENV_2023_2024,
               data = hotspots, 
               family = binomial)

result <- parameters::model_parameters(glm.fit, 
                                       exponentiate = FALSE)

plotly::ggplotly(plot(result) +
       ggplot2::theme(axis.text.y = ggplot2::element_text(size = 8),
                       axis.text.x = ggplot2::element_text(size = 8),
                       axis.title = ggplot2::element_text(size = 8),
                      plot.margin = ggplot2::unit(c(0,0,0,0), "cm")) +
        ggplot2::scale_y_discrete(labels = c("2008-2010",
                                             "2011-2014", 
                                             "2015-2017",
                                             "2018-2019",
                                             "2020-2022",
                                             "2023-2024")))
```
:::

::: {.box .c}
```{r power_law_plot_tuxpan,dpi = 300, warning=FALSE, fig.align = "center", out.width = '100%',out.height='100%',fig.show = "hold"}
# Step 7. make the function por calculate the cumulative ####
funcumsum <- function(x){
    x$cumulative_n <- cumsum(x$n_cases)
    x$perc_cumsum_n <- round((cumsum(x$n_cases)/sum(x$n_cases))*100, digits = 1)
    #x$cumulative_ha <- cumsum(x$ha)
    #x$perc_cumsum_ha <- round((cumsum(x$ha)/sum(x$ha))*100, digits = 1)
    x$id <- 1
    x$id_cumsum <- cumsum(x$id)
    x$id_perc_cum <- round((cumsum(x$id)/nrow(x))*100, digits = 1)
    x
}
# step 8.
data_pareto <- hotspots   |>
    # sf::st_drop_geometry()  |>
    # dplyr::mutate(n_cases = rowSums(dplyr::select(., dplyr::starts_with("DENV"))),
    #              loc = "locality")
    #dplyr::mutate(n_cases = rowSums(dplyr::across(DENV_2008:DENV_2021)),
    #              loc = "locality")  |>
    dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    
    dplyr::select(loc, n_cases, hotspots_gi)  |>
    dplyr::arrange(loc, desc(hotspots_gi), desc(n_cases))  |>
    dplyr::group_by(loc)  |>
    tidyr::nest()  |>
    dplyr::mutate(pareto_cases = purrr::map(data,
                                            funcumsum))  |>
    dplyr::select(-data)  |>
    tidyr::unnest(cols = c(pareto_cases))

# step 4. visualization of pareto rules 
plotly::ggplotly(denhotspots::power_law_plot(x = data_pareto) +
                  ggplot2::theme(axis.text.y = ggplot2::element_text(size = 8),
                                 axis.text.x = ggplot2::element_text(size = 8),
                       axis.title = ggplot2::element_text(size = 8),
                      plot.margin = ggplot2::unit(c(0,0,0,0), "cm")))  |> 
  plotly::layout(showlegend = FALSE)






```
:::

::: {.box .d}
```{r gauge_blocks_tuxpan,fig.align = "center", out.height='90%', out.width = '90%'}
y_hot <- hotspots |> dplyr::filter(hotspots_gi == 1)
centroid <- rgeomex::blocks_ine20_mx_centroid |>
  sf::st_as_sf(coords = c("x", "y"), crs = 4326)
b_loc <- centroid[hotspots, ]
b_hot <- b_loc[y_hot, ]
flexdashboard::gauge(round((nrow(b_hot)/nrow(b_loc))*100, digits = 1),
                     min = 0, max = 100, 
                     symbol = '%', 
                     label = "Manzanas",
                     flexdashboard::gaugeSectors(success = c(0, 30), 
                                                 warning = c(31, 50), 
                                                 danger = c(51, 100),
                                                 colors = c("#11BB33", #"#63C1A0", 
                                                            "#FC8427",
                                                            "#E01A59")))
```
:::

::: {.box .e}
```{r gauge_AGEB_tuxpan, fig.align = "center", out.height='90%', out.width = '90%'}

y <- hotspots  |>
    sf::st_drop_geometry() |>
     dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    dplyr::select(loc, n_cases, hotspots_gi) 
y_hot <- y |>dplyr::filter(hotspots_gi == 1)
  
flexdashboard::gauge(round((nrow(y_hot)/nrow(y))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "AGEBs",
      flexdashboard::gaugeSectors(success = c(0, 30), 
                                  warning = c(31, 50), 
                                  danger = c(51, 100),
                                  colors = c("#11BB33",
                                             "#FC8427",
                                             "#E01A59")))
```
:::

::: {.box .f}
```{r gauge_casos_tuxpan, out.height='90%', out.width = '90%', fig.align = "center"}

y <- hotspots  |>
    sf::st_drop_geometry() |>
      dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    dplyr::select(loc, n_cases, hotspots_gi) 
y_hot <- y |>dplyr::filter(hotspots_gi == 1)

flexdashboard::gauge(round((sum(y_hot$n_cases)/sum(y$n_cases))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "Casos de Dengue",
      flexdashboard::gaugeSectors(success = c(11, 100), 
                                  warning = c(6, 10), 
                                  danger = c(0, 5),
                                  colors = c("#11BB33", 
                                             "#FC8427",
                                             "#E01A59")))
```
:::
:::
</body>
</html>

### [**Poza Rica**]{style="color:#990000"}

<html>
<head>

</head>
<body>
::: wrapper
::: {.box .a}
```{r hotspots_dengue_poza_rica}
# Step 1. extract the locality ####
loc <- rgeomex::extract_locality(cve_edo = "30", 
                                 locality = "Poza Rica del Hidalgo")

# Step 2. Extract the hotspots ####
hotspots <- hotspotsdata::den_hotspots[loc, ]
mapview::mapview(hotspots,
                 zcol = "intensity_gi",
                 layer.name = "Intensidad",
                 label = FALSE,
                 color = "white",
                 lwd = 0.5, 
                 col.regions =  rcartocolor::carto_pal(n = max(hotspots$intensity_gi), 
                                                       name = "OrYel"))

```
:::

::: {.box .b}
```{r forest_plot_poza_rica, dpi = 300, fig.height= 5,fig.width = 7,fig.align = "center", out.height='100%', out.width = '100%',fig.show = "hold"}
 
# Logistic Regression
hotspots <- hotspots |>
    dplyr::mutate(DENV_2008_2010 = DENV_2008 + DENV_2009 + DENV_2010) |>
    dplyr::mutate(DENV_2011_2014 = DENV_2011 + DENV_2012 + DENV_2013 + DENV_2014) |>
    dplyr::mutate(DENV_2015_2017 = DENV_2015 +  DENV_2016 + DENV_2017) |>
    dplyr::mutate(DENV_2018_2019 = DENV_2018 +  DENV_2019) |>
    dplyr::mutate(DENV_2020_2022 = DENV_2020 +  DENV_2021 + DENV_2022) |>
    dplyr::mutate(DENV_2023_2024 = DENV_2023 +  DENV_2024) 


# Logistic Regression
glm.fit <- glm(hotspots_gi~DENV_2008_2010 + DENV_2011_2014 +
                   DENV_2015_2017 + DENV_2018_2019 +
                   DENV_2020_2022 + DENV_2023_2024,
               data = hotspots, 
               family = binomial)

result <- parameters::model_parameters(glm.fit, 
                                       exponentiate = FALSE)

plotly::ggplotly(plot(result) +
       ggplot2::theme(axis.text.y = ggplot2::element_text(size = 8),
                       axis.text.x = ggplot2::element_text(size = 8),
                       axis.title = ggplot2::element_text(size = 8),
                      plot.margin = ggplot2::unit(c(0,0,0,0), "cm")) +
        ggplot2::scale_y_discrete(labels = c("2008-2010",
                                             "2011-2014", 
                                             "2015-2017",
                                             "2018-2019",
                                             "2020-2022",
                                             "2023-2024")))
```
:::

::: {.box .c}
```{r power_law_plot_poza_rica,dpi = 300, warning=FALSE, fig.align = "center", out.width = '100%',out.height='100%',fig.show = "hold"}
# Step 7. make the function por calculate the cumulative ####
funcumsum <- function(x){
    x$cumulative_n <- cumsum(x$n_cases)
    x$perc_cumsum_n <- round((cumsum(x$n_cases)/sum(x$n_cases))*100, digits = 1)
    #x$cumulative_ha <- cumsum(x$ha)
    #x$perc_cumsum_ha <- round((cumsum(x$ha)/sum(x$ha))*100, digits = 1)
    x$id <- 1
    x$id_cumsum <- cumsum(x$id)
    x$id_perc_cum <- round((cumsum(x$id)/nrow(x))*100, digits = 1)
    x
}
# step 8.
data_pareto <- hotspots   |>
    # sf::st_drop_geometry()  |>
    # dplyr::mutate(n_cases = rowSums(dplyr::select(., dplyr::starts_with("DENV"))),
    #              loc = "locality")
    #dplyr::mutate(n_cases = rowSums(dplyr::across(DENV_2008:DENV_2021)),
    #              loc = "locality")  |>
    dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    
    dplyr::select(loc, n_cases, hotspots_gi)  |>
    dplyr::arrange(loc, desc(hotspots_gi), desc(n_cases))  |>
    dplyr::group_by(loc)  |>
    tidyr::nest()  |>
    dplyr::mutate(pareto_cases = purrr::map(data,
                                            funcumsum))  |>
    dplyr::select(-data)  |>
    tidyr::unnest(cols = c(pareto_cases))

# step 4. visualization of pareto rules 
plotly::ggplotly(denhotspots::power_law_plot(x = data_pareto) +
                  ggplot2::theme(axis.text.y = ggplot2::element_text(size = 8),
                                 axis.text.x = ggplot2::element_text(size = 8),
                       axis.title = ggplot2::element_text(size = 8),
                      plot.margin = ggplot2::unit(c(0,0,0,0), "cm")))  |> 
  plotly::layout(showlegend = FALSE)






```
:::

::: {.box .d}
```{r gauge_blocks_poza_rica,fig.align = "center", out.height='90%', out.width = '90%'}
y_hot <- hotspots |> dplyr::filter(hotspots_gi == 1)
centroid <- rgeomex::blocks_ine20_mx_centroid |>
  sf::st_as_sf(coords = c("x", "y"), crs = 4326)
b_loc <- centroid[hotspots, ]
b_hot <- b_loc[y_hot, ]
flexdashboard::gauge(round((nrow(b_hot)/nrow(b_loc))*100, digits = 1),
                     min = 0, max = 100, 
                     symbol = '%', 
                     label = "Manzanas",
                     flexdashboard::gaugeSectors(success = c(0, 30), 
                                                 warning = c(31, 50), 
                                                 danger = c(51, 100),
                                                 colors = c("#11BB33", #"#63C1A0", 
                                                            "#FC8427",
                                                            "#E01A59")))
```
:::

::: {.box .e}
```{r gauge_AGEB_poza_rica, fig.align = "center", out.height='90%', out.width = '90%'}

y <- hotspots  |>
    sf::st_drop_geometry() |>
     dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    dplyr::select(loc, n_cases, hotspots_gi) 
y_hot <- y |>dplyr::filter(hotspots_gi == 1)
  
flexdashboard::gauge(round((nrow(y_hot)/nrow(y))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "AGEBs",
      flexdashboard::gaugeSectors(success = c(0, 30), 
                                  warning = c(31, 50), 
                                  danger = c(51, 100),
                                  colors = c("#11BB33",
                                             "#FC8427",
                                             "#E01A59")))
```
:::

::: {.box .f}
```{r gauge_casos_poza_rica, out.height='90%', out.width = '90%', fig.align = "center"}

y <- hotspots  |>
    sf::st_drop_geometry() |>
      dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    dplyr::select(loc, n_cases, hotspots_gi) 
y_hot <- y |>dplyr::filter(hotspots_gi == 1)

flexdashboard::gauge(round((sum(y_hot$n_cases)/sum(y$n_cases))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "Casos de Dengue",
      flexdashboard::gaugeSectors(success = c(11, 100), 
                                  warning = c(6, 10), 
                                  danger = c(0, 5),
                                  colors = c("#11BB33", 
                                             "#FC8427",
                                             "#E01A59")))
```
:::
:::
</body>
</html>

### [**Papantla**]{style="color:#990000"}

<html>
<head>
</head>
<body>
::: wrapper
::: {.box .a}
```{r hotspots_dengue_papantla}
# Step 1. extract the locality ####
loc <- rgeomex::extract_locality(cve_edo = "30", 
                                 locality = "Papantla de Olearte")

# Step 2. Extract the hotspots ####
hotspots <- hotspotsdata::den_hotspots[loc, ]
mapview::mapview(hotspots,
                 zcol = "intensity_gi",
                 layer.name = "Intensidad",
                 label = FALSE,
                 color = "white",
                 lwd = 0.5, 
                 col.regions =  rcartocolor::carto_pal(n = max(hotspots$intensity_gi), 
                                                       name = "OrYel"))

```
:::

::: {.box .b}
```{r forest_plot_papantla, dpi = 300, fig.height= 5,fig.width = 7,fig.align = "center", out.height='100%', out.width = '100%',fig.show = "hold"}
 
# Logistic Regression
hotspots <- hotspots |>
    dplyr::mutate(DENV_2008_2010 = DENV_2008 + DENV_2009 + DENV_2010) |>
    dplyr::mutate(DENV_2011_2014 = DENV_2011 + DENV_2012 + DENV_2013 + DENV_2014) |>
    dplyr::mutate(DENV_2015_2017 = DENV_2015 +  DENV_2016 + DENV_2017) |>
    dplyr::mutate(DENV_2018_2019 = DENV_2018 +  DENV_2019) |>
    dplyr::mutate(DENV_2020_2022 = DENV_2020 +  DENV_2021 + DENV_2022) |>
    dplyr::mutate(DENV_2023_2024 = DENV_2023 +  DENV_2024) 


# Logistic Regression
glm.fit <- glm(hotspots_gi~DENV_2008_2010 + DENV_2011_2014 +
                   DENV_2015_2017 + DENV_2018_2019 +
                   DENV_2020_2022 + DENV_2023_2024,
               data = hotspots, 
               family = binomial)

result <- parameters::model_parameters(glm.fit, 
                                       exponentiate = FALSE)

plotly::ggplotly(plot(result) +
       ggplot2::theme(axis.text.y = ggplot2::element_text(size = 8),
                       axis.text.x = ggplot2::element_text(size = 8),
                       axis.title = ggplot2::element_text(size = 8),
                      plot.margin = ggplot2::unit(c(0,0,0,0), "cm")) +
        ggplot2::scale_y_discrete(labels = c("2008-2010",
                                             "2011-2014", 
                                             "2015-2017",
                                             "2018-2019",
                                             "2020-2022",
                                             "2023-2024")))
```
:::

::: {.box .c}
```{r power_law_plot_papantla,dpi = 300, warning=FALSE, fig.align = "center", out.width = '100%',out.height='100%',fig.show = "hold"}
# Step 7. make the function por calculate the cumulative ####
funcumsum <- function(x){
    x$cumulative_n <- cumsum(x$n_cases)
    x$perc_cumsum_n <- round((cumsum(x$n_cases)/sum(x$n_cases))*100, digits = 1)
    #x$cumulative_ha <- cumsum(x$ha)
    #x$perc_cumsum_ha <- round((cumsum(x$ha)/sum(x$ha))*100, digits = 1)
    x$id <- 1
    x$id_cumsum <- cumsum(x$id)
    x$id_perc_cum <- round((cumsum(x$id)/nrow(x))*100, digits = 1)
    x
}
# step 8.
data_pareto <- hotspots   |>
    # sf::st_drop_geometry()  |>
    # dplyr::mutate(n_cases = rowSums(dplyr::select(., dplyr::starts_with("DENV"))),
    #              loc = "locality")
    #dplyr::mutate(n_cases = rowSums(dplyr::across(DENV_2008:DENV_2021)),
    #              loc = "locality")  |>
    dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    
    dplyr::select(loc, n_cases, hotspots_gi)  |>
    dplyr::arrange(loc, desc(hotspots_gi), desc(n_cases))  |>
    dplyr::group_by(loc)  |>
    tidyr::nest()  |>
    dplyr::mutate(pareto_cases = purrr::map(data,
                                            funcumsum))  |>
    dplyr::select(-data)  |>
    tidyr::unnest(cols = c(pareto_cases))

# step 4. visualization of pareto rules 
plotly::ggplotly(denhotspots::power_law_plot(x = data_pareto) +
                  ggplot2::theme(axis.text.y = ggplot2::element_text(size = 8),
                                 axis.text.x = ggplot2::element_text(size = 8),
                       axis.title = ggplot2::element_text(size = 8),
                      plot.margin = ggplot2::unit(c(0,0,0,0), "cm")))  |> 
  plotly::layout(showlegend = FALSE)






```
:::

::: {.box .d}
```{r gauge_blocks_papantla,fig.align = "center", out.height='90%', out.width = '90%'}
y_hot <- hotspots |> dplyr::filter(hotspots_gi == 1)
centroid <- rgeomex::blocks_ine20_mx_centroid |>
  sf::st_as_sf(coords = c("x", "y"), crs = 4326)
b_loc <- centroid[hotspots, ]
b_hot <- b_loc[y_hot, ]
flexdashboard::gauge(round((nrow(b_hot)/nrow(b_loc))*100, digits = 1),
                     min = 0, max = 100, 
                     symbol = '%', 
                     label = "Manzanas",
                     flexdashboard::gaugeSectors(success = c(0, 30), 
                                                 warning = c(31, 50), 
                                                 danger = c(51, 100),
                                                 colors = c("#11BB33", #"#63C1A0", 
                                                            "#FC8427",
                                                            "#E01A59")))
```
:::

::: {.box .e}
```{r gauge_AGEB_papantla, fig.align = "center", out.height='90%', out.width = '90%'}

y <- hotspots  |>
    sf::st_drop_geometry() |>
     dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    dplyr::select(loc, n_cases, hotspots_gi) 
y_hot <- y |>dplyr::filter(hotspots_gi == 1)
  
flexdashboard::gauge(round((nrow(y_hot)/nrow(y))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "AGEBs",
      flexdashboard::gaugeSectors(success = c(0, 30), 
                                  warning = c(31, 50), 
                                  danger = c(51, 100),
                                  colors = c("#11BB33",
                                             "#FC8427",
                                             "#E01A59")))
```
:::

::: {.box .f}
```{r gauge_casos_papantla, out.height='90%', out.width = '90%', fig.align = "center"}

y <- hotspots  |>
    sf::st_drop_geometry() |>
      dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    dplyr::select(loc, n_cases, hotspots_gi) 
y_hot <- y |>dplyr::filter(hotspots_gi == 1)

flexdashboard::gauge(round((sum(y_hot$n_cases)/sum(y$n_cases))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "Casos de Dengue",
      flexdashboard::gaugeSectors(success = c(11, 100), 
                                  warning = c(6, 10), 
                                  danger = c(0, 5),
                                  colors = c("#11BB33", 
                                             "#FC8427",
                                             "#E01A59")))
```
:::
:::
</body>
</html>


### [**Martinez de la Torre**]{style="color:#990000"}

<html>
<head>
</head>
<body>
::: wrapper
::: {.box .a}
```{r hotspots_dengue_martinez}
# Step 1. extract the locality ####
loc <- rgeomex::extract_locality(cve_edo = "30", 
                                 locality = "Martinez de la Torre")

# Step 2. Extract the hotspots ####
hotspots <- hotspotsdata::den_hotspots[loc, ]
mapview::mapview(hotspots,
                 zcol = "intensity_gi",
                 layer.name = "Intensidad",
                 label = FALSE,
                 color = "white",
                 lwd = 0.5, 
                 col.regions =  rcartocolor::carto_pal(n = max(hotspots$intensity_gi), 
                                                       name = "OrYel"))

```
:::

::: {.box .b}
```{r forest_plot_martinez, dpi = 300, fig.height= 5,fig.width = 7,fig.align = "center", out.height='100%', out.width = '100%',fig.show = "hold"}
 
# Logistic Regression
hotspots <- hotspots |>
    dplyr::mutate(DENV_2008_2010 = DENV_2008 + DENV_2009 + DENV_2010) |>
    dplyr::mutate(DENV_2011_2014 = DENV_2011 + DENV_2012 + DENV_2013 + DENV_2014) |>
    dplyr::mutate(DENV_2015_2017 = DENV_2015 +  DENV_2016 + DENV_2017) |>
    dplyr::mutate(DENV_2018_2019 = DENV_2018 +  DENV_2019) |>
    dplyr::mutate(DENV_2020_2022 = DENV_2020 +  DENV_2021 + DENV_2022) |>
    dplyr::mutate(DENV_2023_2024 = DENV_2023 +  DENV_2024) 


# Logistic Regression
glm.fit <- glm(hotspots_gi~DENV_2008_2010 + DENV_2011_2014 +
                   DENV_2015_2017 + DENV_2018_2019 +
                   DENV_2020_2022 + DENV_2023_2024,
               data = hotspots, 
               family = binomial)

result <- parameters::model_parameters(glm.fit, 
                                       exponentiate = FALSE)

plotly::ggplotly(plot(result) +
       ggplot2::theme(axis.text.y = ggplot2::element_text(size = 8),
                       axis.text.x = ggplot2::element_text(size = 8),
                       axis.title = ggplot2::element_text(size = 8),
                      plot.margin = ggplot2::unit(c(0,0,0,0), "cm")) +
        ggplot2::scale_y_discrete(labels = c("2008-2010",
                                             "2011-2014", 
                                             "2015-2017",
                                             "2018-2019",
                                             "2020-2022",
                                             "2023-2024")))
```
:::

::: {.box .c}
```{r power_law_plot_martinez,dpi = 300, warning=FALSE, fig.align = "center", out.width = '100%',out.height='100%',fig.show = "hold"}
# Step 7. make the function por calculate the cumulative ####
funcumsum <- function(x){
    x$cumulative_n <- cumsum(x$n_cases)
    x$perc_cumsum_n <- round((cumsum(x$n_cases)/sum(x$n_cases))*100, digits = 1)
    #x$cumulative_ha <- cumsum(x$ha)
    #x$perc_cumsum_ha <- round((cumsum(x$ha)/sum(x$ha))*100, digits = 1)
    x$id <- 1
    x$id_cumsum <- cumsum(x$id)
    x$id_perc_cum <- round((cumsum(x$id)/nrow(x))*100, digits = 1)
    x
}
# step 8.
data_pareto <- hotspots   |>
    # sf::st_drop_geometry()  |>
    # dplyr::mutate(n_cases = rowSums(dplyr::select(., dplyr::starts_with("DENV"))),
    #              loc = "locality")
    #dplyr::mutate(n_cases = rowSums(dplyr::across(DENV_2008:DENV_2021)),
    #              loc = "locality")  |>
    dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    
    dplyr::select(loc, n_cases, hotspots_gi)  |>
    dplyr::arrange(loc, desc(hotspots_gi), desc(n_cases))  |>
    dplyr::group_by(loc)  |>
    tidyr::nest()  |>
    dplyr::mutate(pareto_cases = purrr::map(data,
                                            funcumsum))  |>
    dplyr::select(-data)  |>
    tidyr::unnest(cols = c(pareto_cases))

# step 4. visualization of pareto rules 
plotly::ggplotly(denhotspots::power_law_plot(x = data_pareto) +
                  ggplot2::theme(axis.text.y = ggplot2::element_text(size = 8),
                                 axis.text.x = ggplot2::element_text(size = 8),
                       axis.title = ggplot2::element_text(size = 8),
                      plot.margin = ggplot2::unit(c(0,0,0,0), "cm")))  |> 
  plotly::layout(showlegend = FALSE)






```
:::

::: {.box .d}
```{r gauge_blocks_martinez,fig.align = "center", out.height='90%', out.width = '90%'}
y_hot <- hotspots |> dplyr::filter(hotspots_gi == 1)
centroid <- rgeomex::blocks_ine20_mx_centroid |>
  sf::st_as_sf(coords = c("x", "y"), crs = 4326)
b_loc <- centroid[hotspots, ]
b_hot <- b_loc[y_hot, ]
flexdashboard::gauge(round((nrow(b_hot)/nrow(b_loc))*100, digits = 1),
                     min = 0, max = 100, 
                     symbol = '%', 
                     label = "Manzanas",
                     flexdashboard::gaugeSectors(success = c(0, 30), 
                                                 warning = c(31, 50), 
                                                 danger = c(51, 100),
                                                 colors = c("#11BB33", #"#63C1A0", 
                                                            "#FC8427",
                                                            "#E01A59")))
```
:::

::: {.box .e}
```{r gauge_AGEB_martinez, fig.align = "center", out.height='90%', out.width = '90%'}

y <- hotspots  |>
    sf::st_drop_geometry() |>
     dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    dplyr::select(loc, n_cases, hotspots_gi) 
y_hot <- y |>dplyr::filter(hotspots_gi == 1)
  
flexdashboard::gauge(round((nrow(y_hot)/nrow(y))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "AGEBs",
      flexdashboard::gaugeSectors(success = c(0, 30), 
                                  warning = c(31, 50), 
                                  danger = c(51, 100),
                                  colors = c("#11BB33",
                                             "#FC8427",
                                             "#E01A59")))
```
:::

::: {.box .f}
```{r gauge_casos_martinez, out.height='90%', out.width = '90%', fig.align = "center"}

y <- hotspots  |>
    sf::st_drop_geometry() |>
      dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    dplyr::select(loc, n_cases, hotspots_gi) 
y_hot <- y |>dplyr::filter(hotspots_gi == 1)

flexdashboard::gauge(round((sum(y_hot$n_cases)/sum(y$n_cases))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "Casos de Dengue",
      flexdashboard::gaugeSectors(success = c(11, 100), 
                                  warning = c(6, 10), 
                                  danger = c(0, 5),
                                  colors = c("#11BB33", 
                                             "#FC8427",
                                             "#E01A59")))
```
:::
:::
</body>
</html>


### [**Xalapa**]{style="color:#990000"}

<html>
<head>

</head>
<body>
::: wrapper
::: {.box .a}
```{r hotspots_dengue_xalapa}
# Step 1. extract the locality ####
loc <- rgeomex::extract_locality(cve_edo = "30", 
                                 locality = "Xalapa de Ordonez")

# Step 2. Extract the hotspots ####
hotspots <- hotspotsdata::den_hotspots[loc, ]
mapview::mapview(hotspots,
                 zcol = "intensity_gi",
                 layer.name = "Intensidad",
                 label = FALSE,
                 color = "white",
                 lwd = 0.5, 
                 col.regions =  rcartocolor::carto_pal(n = max(hotspots$intensity_gi), 
                                                       name = "OrYel"))

```
:::

::: {.box .b}
```{r forest_plot_xalapa, dpi = 300, fig.height= 5,fig.width = 7,fig.align = "center", out.height='100%', out.width = '100%',fig.show = "hold"}
 
# Logistic Regression
hotspots <- hotspots |>
    dplyr::mutate(DENV_2008_2010 = DENV_2008 + DENV_2009 + DENV_2010) |>
    dplyr::mutate(DENV_2011_2014 = DENV_2011 + DENV_2012 + DENV_2013 + DENV_2014) |>
    dplyr::mutate(DENV_2015_2017 = DENV_2015 +  DENV_2016 + DENV_2017) |>
    dplyr::mutate(DENV_2018_2019 = DENV_2018 +  DENV_2019) |>
    dplyr::mutate(DENV_2020_2022 = DENV_2020 +  DENV_2021 + DENV_2022) |>
    dplyr::mutate(DENV_2023_2024 = DENV_2023 +  DENV_2024) 


# Logistic Regression
glm.fit <- glm(hotspots_gi~DENV_2008_2010 + DENV_2011_2014 +
                   DENV_2015_2017 + DENV_2018_2019 +
                   DENV_2020_2022 + DENV_2023_2024,
               data = hotspots, 
               family = binomial)

result <- parameters::model_parameters(glm.fit, 
                                       exponentiate = FALSE)

plotly::ggplotly(plot(result) +
       ggplot2::theme(axis.text.y = ggplot2::element_text(size = 8),
                       axis.text.x = ggplot2::element_text(size = 8),
                       axis.title = ggplot2::element_text(size = 8),
                      plot.margin = ggplot2::unit(c(0,0,0,0), "cm")) +
        ggplot2::scale_y_discrete(labels = c("2008-2010",
                                             "2011-2014", 
                                             "2015-2017",
                                             "2018-2019",
                                             "2020-2022",
                                             "2023-2024")))
```
:::

::: {.box .c}
```{r power_law_plot_xalapa,dpi = 300, warning=FALSE, fig.align = "center", out.width = '100%',out.height='100%',fig.show = "hold"}
# Step 7. make the function por calculate the cumulative ####
funcumsum <- function(x){
    x$cumulative_n <- cumsum(x$n_cases)
    x$perc_cumsum_n <- round((cumsum(x$n_cases)/sum(x$n_cases))*100, digits = 1)
    #x$cumulative_ha <- cumsum(x$ha)
    #x$perc_cumsum_ha <- round((cumsum(x$ha)/sum(x$ha))*100, digits = 1)
    x$id <- 1
    x$id_cumsum <- cumsum(x$id)
    x$id_perc_cum <- round((cumsum(x$id)/nrow(x))*100, digits = 1)
    x
}
# step 8.
data_pareto <- hotspots   |>
    # sf::st_drop_geometry()  |>
    # dplyr::mutate(n_cases = rowSums(dplyr::select(., dplyr::starts_with("DENV"))),
    #              loc = "locality")
    #dplyr::mutate(n_cases = rowSums(dplyr::across(DENV_2008:DENV_2021)),
    #              loc = "locality")  |>
    dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    
    dplyr::select(loc, n_cases, hotspots_gi)  |>
    dplyr::arrange(loc, desc(hotspots_gi), desc(n_cases))  |>
    dplyr::group_by(loc)  |>
    tidyr::nest()  |>
    dplyr::mutate(pareto_cases = purrr::map(data,
                                            funcumsum))  |>
    dplyr::select(-data)  |>
    tidyr::unnest(cols = c(pareto_cases))

# step 4. visualization of pareto rules 
plotly::ggplotly(denhotspots::power_law_plot(x = data_pareto) +
                  ggplot2::theme(axis.text.y = ggplot2::element_text(size = 8),
                                 axis.text.x = ggplot2::element_text(size = 8),
                       axis.title = ggplot2::element_text(size = 8),
                      plot.margin = ggplot2::unit(c(0,0,0,0), "cm")))  |> 
  plotly::layout(showlegend = FALSE)






```
:::

::: {.box .d}
```{r gauge_blocks_xalapa,fig.align = "center", out.height='90%', out.width = '90%'}
y_hot <- hotspots |> dplyr::filter(hotspots_gi == 1)
centroid <- rgeomex::blocks_ine20_mx_centroid |>
  sf::st_as_sf(coords = c("x", "y"), crs = 4326)
b_loc <- centroid[hotspots, ]
b_hot <- b_loc[y_hot, ]
flexdashboard::gauge(round((nrow(b_hot)/nrow(b_loc))*100, digits = 1),
                     min = 0, max = 100, 
                     symbol = '%', 
                     label = "Manzanas",
                     flexdashboard::gaugeSectors(success = c(0, 30), 
                                                 warning = c(31, 50), 
                                                 danger = c(51, 100),
                                                 colors = c("#11BB33", #"#63C1A0", 
                                                            "#FC8427",
                                                            "#E01A59")))
```
:::

::: {.box .e}
```{r gauge_AGEB_xalapa, fig.align = "center", out.height='90%', out.width = '90%'}

y <- hotspots  |>
    sf::st_drop_geometry() |>
     dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    dplyr::select(loc, n_cases, hotspots_gi) 
y_hot <- y |>dplyr::filter(hotspots_gi == 1)
  
flexdashboard::gauge(round((nrow(y_hot)/nrow(y))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "AGEBs",
      flexdashboard::gaugeSectors(success = c(0, 30), 
                                  warning = c(31, 50), 
                                  danger = c(51, 100),
                                  colors = c("#11BB33",
                                             "#FC8427",
                                             "#E01A59")))
```
:::

::: {.box .f}
```{r gauge_casos_xalapa, out.height='90%', out.width = '90%', fig.align = "center"}

y <- hotspots  |>
    sf::st_drop_geometry() |>
      dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    dplyr::select(loc, n_cases, hotspots_gi) 
y_hot <- y |>dplyr::filter(hotspots_gi == 1)

flexdashboard::gauge(round((sum(y_hot$n_cases)/sum(y$n_cases))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "Casos de Dengue",
      flexdashboard::gaugeSectors(success = c(11, 100), 
                                  warning = c(6, 10), 
                                  danger = c(0, 5),
                                  colors = c("#11BB33", 
                                             "#FC8427",
                                             "#E01A59")))
```
:::
:::
</body>
</html>

### [**C칩rdoba**]{style="color:#990000"}

<html>
<head>
</head>
<body>
::: wrapper
::: {.box .a}
```{r hotspots_dengue_cordoba}
# Step 1. extract the locality ####
loc <- rgeomex::extract_locality(cve_edo = "30", 
                                 locality = "Cordoba")

# Step 2. Extract the hotspots ####
hotspots <- hotspotsdata::den_hotspots[loc, ]
mapview::mapview(hotspots,
                 zcol = "intensity_gi",
                 layer.name = "Intensidad",
                 label = FALSE,
                 color = "white",
                 lwd = 0.5, 
                 col.regions =  rcartocolor::carto_pal(n = max(hotspots$intensity_gi), 
                                                       name = "OrYel"))

```
:::

::: {.box .b}
```{r forest_plot_cordoba, dpi = 300, fig.height= 5,fig.width = 7,fig.align = "center", out.height='100%', out.width = '100%',fig.show = "hold"}
 
# Logistic Regression
hotspots <- hotspots |>
    dplyr::mutate(DENV_2008_2010 = DENV_2008 + DENV_2009 + DENV_2010) |>
    dplyr::mutate(DENV_2011_2014 = DENV_2011 + DENV_2012 + DENV_2013 + DENV_2014) |>
    dplyr::mutate(DENV_2015_2017 = DENV_2015 +  DENV_2016 + DENV_2017) |>
    dplyr::mutate(DENV_2018_2019 = DENV_2018 +  DENV_2019) |>
    dplyr::mutate(DENV_2020_2022 = DENV_2020 +  DENV_2021 + DENV_2022) |>
    dplyr::mutate(DENV_2023_2024 = DENV_2023 +  DENV_2024) 


# Logistic Regression
glm.fit <- glm(hotspots_gi~DENV_2008_2010 + DENV_2011_2014 +
                   DENV_2015_2017 + DENV_2018_2019 +
                   DENV_2020_2022 + DENV_2023_2024,
               data = hotspots, 
               family = binomial)

result <- parameters::model_parameters(glm.fit, 
                                       exponentiate = FALSE)

plotly::ggplotly(plot(result) +
       ggplot2::theme(axis.text.y = ggplot2::element_text(size = 8),
                       axis.text.x = ggplot2::element_text(size = 8),
                       axis.title = ggplot2::element_text(size = 8),
                      plot.margin = ggplot2::unit(c(0,0,0,0), "cm")) +
        ggplot2::scale_y_discrete(labels = c("2008-2010",
                                             "2011-2014", 
                                             "2015-2017",
                                             "2018-2019",
                                             "2020-2022",
                                             "2023-2024")))
```
:::

::: {.box .c}
```{r power_law_plot_cordoba,dpi = 300, warning=FALSE, fig.align = "center", out.width = '100%',out.height='100%',fig.show = "hold"}
# Step 7. make the function por calculate the cumulative ####
funcumsum <- function(x){
    x$cumulative_n <- cumsum(x$n_cases)
    x$perc_cumsum_n <- round((cumsum(x$n_cases)/sum(x$n_cases))*100, digits = 1)
    #x$cumulative_ha <- cumsum(x$ha)
    #x$perc_cumsum_ha <- round((cumsum(x$ha)/sum(x$ha))*100, digits = 1)
    x$id <- 1
    x$id_cumsum <- cumsum(x$id)
    x$id_perc_cum <- round((cumsum(x$id)/nrow(x))*100, digits = 1)
    x
}
# step 8.
data_pareto <- hotspots   |>
    # sf::st_drop_geometry()  |>
    # dplyr::mutate(n_cases = rowSums(dplyr::select(., dplyr::starts_with("DENV"))),
    #              loc = "locality")
    #dplyr::mutate(n_cases = rowSums(dplyr::across(DENV_2008:DENV_2021)),
    #              loc = "locality")  |>
    dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    
    dplyr::select(loc, n_cases, hotspots_gi)  |>
    dplyr::arrange(loc, desc(hotspots_gi), desc(n_cases))  |>
    dplyr::group_by(loc)  |>
    tidyr::nest()  |>
    dplyr::mutate(pareto_cases = purrr::map(data,
                                            funcumsum))  |>
    dplyr::select(-data)  |>
    tidyr::unnest(cols = c(pareto_cases))

# step 4. visualization of pareto rules 
plotly::ggplotly(denhotspots::power_law_plot(x = data_pareto) +
                  ggplot2::theme(axis.text.y = ggplot2::element_text(size = 8),
                                 axis.text.x = ggplot2::element_text(size = 8),
                       axis.title = ggplot2::element_text(size = 8),
                      plot.margin = ggplot2::unit(c(0,0,0,0), "cm")))  |> 
  plotly::layout(showlegend = FALSE)






```
:::

::: {.box .d}
```{r gauge_blocks_cordoba,fig.align = "center", out.height='90%', out.width = '90%'}
y_hot <- hotspots |> dplyr::filter(hotspots_gi == 1)
centroid <- rgeomex::blocks_ine20_mx_centroid |>
  sf::st_as_sf(coords = c("x", "y"), crs = 4326)
b_loc <- centroid[hotspots, ]
b_hot <- b_loc[y_hot, ]
flexdashboard::gauge(round((nrow(b_hot)/nrow(b_loc))*100, digits = 1),
                     min = 0, max = 100, 
                     symbol = '%', 
                     label = "Manzanas",
                     flexdashboard::gaugeSectors(success = c(0, 30), 
                                                 warning = c(31, 50), 
                                                 danger = c(51, 100),
                                                 colors = c("#11BB33", #"#63C1A0", 
                                                            "#FC8427",
                                                            "#E01A59")))
```
:::

::: {.box .e}
```{r gauge_AGEB_cordoba, fig.align = "center", out.height='90%', out.width = '90%'}

y <- hotspots  |>
    sf::st_drop_geometry() |>
     dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    dplyr::select(loc, n_cases, hotspots_gi) 
y_hot <- y |>dplyr::filter(hotspots_gi == 1)
  
flexdashboard::gauge(round((nrow(y_hot)/nrow(y))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "AGEBs",
      flexdashboard::gaugeSectors(success = c(0, 30), 
                                  warning = c(31, 50), 
                                  danger = c(51, 100),
                                  colors = c("#11BB33",
                                             "#FC8427",
                                             "#E01A59")))
```
:::

::: {.box .f}
```{r gauge_casos_cordoba, out.height='90%', out.width = '90%', fig.align = "center"}

y <- hotspots  |>
    sf::st_drop_geometry() |>
      dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    dplyr::select(loc, n_cases, hotspots_gi) 
y_hot <- y |>dplyr::filter(hotspots_gi == 1)

flexdashboard::gauge(round((sum(y_hot$n_cases)/sum(y$n_cases))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "Casos de Dengue",
      flexdashboard::gaugeSectors(success = c(11, 100), 
                                  warning = c(6, 10), 
                                  danger = c(0, 5),
                                  colors = c("#11BB33", 
                                             "#FC8427",
                                             "#E01A59")))
```
:::
:::
</body>
</html>


### [**Orizaba**]{style="color:#990000"}

<html>
<head>
</head>
<body>
::: wrapper
::: {.box .a}
```{r hotspots_dengue_orizaba}
# Step 1. extract the locality ####
loc <- rgeomex::extract_locality(cve_edo = "30", 
                                 locality = "Orizaba")

# Step 2. Extract the hotspots ####
hotspots <- hotspotsdata::den_hotspots[loc, ]
mapview::mapview(hotspots,
                 zcol = "intensity_gi",
                 layer.name = "Intensidad",
                 label = FALSE,
                 color = "white",
                 lwd = 0.5, 
                 col.regions =  rcartocolor::carto_pal(n = max(hotspots$intensity_gi), 
                                                       name = "OrYel"))

```
:::

::: {.box .b}
```{r forest_plot_orizaba, dpi = 300, fig.height= 5,fig.width = 7,fig.align = "center", out.height='100%', out.width = '100%',fig.show = "hold"}
 
# Logistic Regression
hotspots <- hotspots |>
    dplyr::mutate(DENV_2008_2010 = DENV_2008 + DENV_2009 + DENV_2010) |>
    dplyr::mutate(DENV_2011_2014 = DENV_2011 + DENV_2012 + DENV_2013 + DENV_2014) |>
    dplyr::mutate(DENV_2015_2017 = DENV_2015 +  DENV_2016 + DENV_2017) |>
    dplyr::mutate(DENV_2018_2019 = DENV_2018 +  DENV_2019) |>
    dplyr::mutate(DENV_2020_2022 = DENV_2020 +  DENV_2021 + DENV_2022) |>
    dplyr::mutate(DENV_2023_2024 = DENV_2023 +  DENV_2024) 


# Logistic Regression
glm.fit <- glm(hotspots_gi~DENV_2008_2010 + DENV_2011_2014 +
                   DENV_2015_2017 + DENV_2018_2019 +
                   DENV_2020_2022 + DENV_2023_2024,
               data = hotspots, 
               family = binomial)

result <- parameters::model_parameters(glm.fit, 
                                       exponentiate = FALSE)

plotly::ggplotly(plot(result) +
       ggplot2::theme(axis.text.y = ggplot2::element_text(size = 8),
                       axis.text.x = ggplot2::element_text(size = 8),
                       axis.title = ggplot2::element_text(size = 8),
                      plot.margin = ggplot2::unit(c(0,0,0,0), "cm")) +
        ggplot2::scale_y_discrete(labels = c("2008-2010",
                                             "2011-2014", 
                                             "2015-2017",
                                             "2018-2019",
                                             "2020-2022",
                                             "2023-2024")))
```
:::

::: {.box .c}
```{r power_law_plot_orizaba,dpi = 300, warning=FALSE, fig.align = "center", out.width = '100%',out.height='100%',fig.show = "hold"}
# Step 7. make the function por calculate the cumulative ####
funcumsum <- function(x){
    x$cumulative_n <- cumsum(x$n_cases)
    x$perc_cumsum_n <- round((cumsum(x$n_cases)/sum(x$n_cases))*100, digits = 1)
    #x$cumulative_ha <- cumsum(x$ha)
    #x$perc_cumsum_ha <- round((cumsum(x$ha)/sum(x$ha))*100, digits = 1)
    x$id <- 1
    x$id_cumsum <- cumsum(x$id)
    x$id_perc_cum <- round((cumsum(x$id)/nrow(x))*100, digits = 1)
    x
}
# step 8.
data_pareto <- hotspots   |>
    # sf::st_drop_geometry()  |>
    # dplyr::mutate(n_cases = rowSums(dplyr::select(., dplyr::starts_with("DENV"))),
    #              loc = "locality")
    #dplyr::mutate(n_cases = rowSums(dplyr::across(DENV_2008:DENV_2021)),
    #              loc = "locality")  |>
    dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    
    dplyr::select(loc, n_cases, hotspots_gi)  |>
    dplyr::arrange(loc, desc(hotspots_gi), desc(n_cases))  |>
    dplyr::group_by(loc)  |>
    tidyr::nest()  |>
    dplyr::mutate(pareto_cases = purrr::map(data,
                                            funcumsum))  |>
    dplyr::select(-data)  |>
    tidyr::unnest(cols = c(pareto_cases))

# step 4. visualization of pareto rules 
plotly::ggplotly(denhotspots::power_law_plot(x = data_pareto) +
                  ggplot2::theme(axis.text.y = ggplot2::element_text(size = 8),
                                 axis.text.x = ggplot2::element_text(size = 8),
                       axis.title = ggplot2::element_text(size = 8),
                      plot.margin = ggplot2::unit(c(0,0,0,0), "cm")))  |> 
  plotly::layout(showlegend = FALSE)






```
:::

::: {.box .d}
```{r gauge_blocks_orizaba,fig.align = "center", out.height='90%', out.width = '90%'}
y_hot <- hotspots |> dplyr::filter(hotspots_gi == 1)
centroid <- rgeomex::blocks_ine20_mx_centroid |>
  sf::st_as_sf(coords = c("x", "y"), crs = 4326)
b_loc <- centroid[hotspots, ]
b_hot <- b_loc[y_hot, ]
flexdashboard::gauge(round((nrow(b_hot)/nrow(b_loc))*100, digits = 1),
                     min = 0, max = 100, 
                     symbol = '%', 
                     label = "Manzanas",
                     flexdashboard::gaugeSectors(success = c(0, 30), 
                                                 warning = c(31, 50), 
                                                 danger = c(51, 100),
                                                 colors = c("#11BB33", #"#63C1A0", 
                                                            "#FC8427",
                                                            "#E01A59")))
```
:::

::: {.box .e}
```{r gauge_AGEB_orizaba, fig.align = "center", out.height='90%', out.width = '90%'}

y <- hotspots  |>
    sf::st_drop_geometry() |>
     dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    dplyr::select(loc, n_cases, hotspots_gi) 
y_hot <- y |>dplyr::filter(hotspots_gi == 1)
  
flexdashboard::gauge(round((nrow(y_hot)/nrow(y))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "AGEBs",
      flexdashboard::gaugeSectors(success = c(0, 30), 
                                  warning = c(31, 50), 
                                  danger = c(51, 100),
                                  colors = c("#11BB33",
                                             "#FC8427",
                                             "#E01A59")))
```
:::

::: {.box .f}
```{r gauge_casos_orizaba, out.height='90%', out.width = '90%', fig.align = "center"}

y <- hotspots  |>
    sf::st_drop_geometry() |>
      dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    dplyr::select(loc, n_cases, hotspots_gi) 
y_hot <- y |>dplyr::filter(hotspots_gi == 1)

flexdashboard::gauge(round((sum(y_hot$n_cases)/sum(y$n_cases))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "Casos de Dengue",
      flexdashboard::gaugeSectors(success = c(11, 100), 
                                  warning = c(6, 10), 
                                  danger = c(0, 5),
                                  colors = c("#11BB33", 
                                             "#FC8427",
                                             "#E01A59")))
```
:::
:::
</body>
</html>


### [**Veracruz**]{style="color:#990000"}

<html>
<head>
</head>
<body>
::: wrapper
::: {.box .a}
```{r hotspots_dengue_veracruz}
# Step 1. extract the locality ####
loc <- rgeomex::extract_locality(cve_edo = "30", 
                                 locality = c("Verucruz",
                                              "Bocal del Rio"))

# Step 2. Extract the hotspots ####
hotspots <- hotspotsdata::den_hotspots[loc, ]
mapview::mapview(hotspots,
                 zcol = "intensity_gi",
                 layer.name = "Intensidad",
                 label = FALSE,
                 color = "white",
                 lwd = 0.5, 
                 col.regions =  rcartocolor::carto_pal(n = max(hotspots$intensity_gi), 
                                                       name = "OrYel"))

```
:::

::: {.box .b}
```{r forest_plot_veracruz, dpi = 300, fig.height= 5,fig.width = 7,fig.align = "center", out.height='100%', out.width = '100%',fig.show = "hold"}
 
# Logistic Regression
hotspots <- hotspots |>
    dplyr::mutate(DENV_2008_2010 = DENV_2008 + DENV_2009 + DENV_2010) |>
    dplyr::mutate(DENV_2011_2014 = DENV_2011 + DENV_2012 + DENV_2013 + DENV_2014) |>
    dplyr::mutate(DENV_2015_2017 = DENV_2015 +  DENV_2016 + DENV_2017) |>
    dplyr::mutate(DENV_2018_2019 = DENV_2018 +  DENV_2019) |>
    dplyr::mutate(DENV_2020_2022 = DENV_2020 +  DENV_2021 + DENV_2022) |>
    dplyr::mutate(DENV_2023_2024 = DENV_2023 +  DENV_2024) 


# Logistic Regression
glm.fit <- glm(hotspots_gi~DENV_2008_2010 + DENV_2011_2014 +
                   DENV_2015_2017 + DENV_2018_2019 +
                   DENV_2020_2022 + DENV_2023_2024,
               data = hotspots, 
               family = binomial)

result <- parameters::model_parameters(glm.fit, 
                                       exponentiate = FALSE)

plotly::ggplotly(plot(result) +
       ggplot2::theme(axis.text.y = ggplot2::element_text(size = 8),
                       axis.text.x = ggplot2::element_text(size = 8),
                       axis.title = ggplot2::element_text(size = 8),
                      plot.margin = ggplot2::unit(c(0,0,0,0), "cm")) +
        ggplot2::scale_y_discrete(labels = c("2008-2010",
                                             "2011-2014", 
                                             "2015-2017",
                                             "2018-2019",
                                             "2020-2022",
                                             "2023-2024")))
```
:::

::: {.box .c}
```{r power_law_plot_veracruz,dpi = 300, warning=FALSE, fig.align = "center", out.width = '100%',out.height='100%',fig.show = "hold"}
# Step 7. make the function por calculate the cumulative ####
funcumsum <- function(x){
    x$cumulative_n <- cumsum(x$n_cases)
    x$perc_cumsum_n <- round((cumsum(x$n_cases)/sum(x$n_cases))*100, digits = 1)
    #x$cumulative_ha <- cumsum(x$ha)
    #x$perc_cumsum_ha <- round((cumsum(x$ha)/sum(x$ha))*100, digits = 1)
    x$id <- 1
    x$id_cumsum <- cumsum(x$id)
    x$id_perc_cum <- round((cumsum(x$id)/nrow(x))*100, digits = 1)
    x
}
# step 8.
data_pareto <- hotspots   |>
    # sf::st_drop_geometry()  |>
    # dplyr::mutate(n_cases = rowSums(dplyr::select(., dplyr::starts_with("DENV"))),
    #              loc = "locality")
    #dplyr::mutate(n_cases = rowSums(dplyr::across(DENV_2008:DENV_2021)),
    #              loc = "locality")  |>
    dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    
    dplyr::select(loc, n_cases, hotspots_gi)  |>
    dplyr::arrange(loc, desc(hotspots_gi), desc(n_cases))  |>
    dplyr::group_by(loc)  |>
    tidyr::nest()  |>
    dplyr::mutate(pareto_cases = purrr::map(data,
                                            funcumsum))  |>
    dplyr::select(-data)  |>
    tidyr::unnest(cols = c(pareto_cases))

# step 4. visualization of pareto rules 
plotly::ggplotly(denhotspots::power_law_plot(x = data_pareto) +
                  ggplot2::theme(axis.text.y = ggplot2::element_text(size = 8),
                                 axis.text.x = ggplot2::element_text(size = 8),
                       axis.title = ggplot2::element_text(size = 8),
                      plot.margin = ggplot2::unit(c(0,0,0,0), "cm")))  |> 
  plotly::layout(showlegend = FALSE)






```
:::

::: {.box .d}
```{r gauge_blocks_veracruz,fig.align = "center", out.height='90%', out.width = '90%'}
y_hot <- hotspots |> dplyr::filter(hotspots_gi == 1)
centroid <- rgeomex::blocks_ine20_mx_centroid |>
  sf::st_as_sf(coords = c("x", "y"), crs = 4326)
b_loc <- centroid[hotspots, ]
b_hot <- b_loc[y_hot, ]
flexdashboard::gauge(round((nrow(b_hot)/nrow(b_loc))*100, digits = 1),
                     min = 0, max = 100, 
                     symbol = '%', 
                     label = "Manzanas",
                     flexdashboard::gaugeSectors(success = c(0, 30), 
                                                 warning = c(31, 50), 
                                                 danger = c(51, 100),
                                                 colors = c("#11BB33", #"#63C1A0", 
                                                            "#FC8427",
                                                            "#E01A59")))
```
:::

::: {.box .e}
```{r gauge_AGEB_veracruz, fig.align = "center", out.height='90%', out.width = '90%'}

y <- hotspots  |>
    sf::st_drop_geometry() |>
     dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    dplyr::select(loc, n_cases, hotspots_gi) 
y_hot <- y |>dplyr::filter(hotspots_gi == 1)
  
flexdashboard::gauge(round((nrow(y_hot)/nrow(y))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "AGEBs",
      flexdashboard::gaugeSectors(success = c(0, 30), 
                                  warning = c(31, 50), 
                                  danger = c(51, 100),
                                  colors = c("#11BB33",
                                             "#FC8427",
                                             "#E01A59")))
```
:::

::: {.box .f}
```{r gauge_casos_veracruz, out.height='90%', out.width = '90%', fig.align = "center"}

y <- hotspots  |>
    sf::st_drop_geometry() |>
      dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    dplyr::select(loc, n_cases, hotspots_gi) 
y_hot <- y |>dplyr::filter(hotspots_gi == 1)

flexdashboard::gauge(round((sum(y_hot$n_cases)/sum(y$n_cases))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "Casos de Dengue",
      flexdashboard::gaugeSectors(success = c(11, 100), 
                                  warning = c(6, 10), 
                                  danger = c(0, 5),
                                  colors = c("#11BB33", 
                                             "#FC8427",
                                             "#E01A59")))
```
:::
:::
</body>
</html>

### [**Cosamaloapan**]{style="color:#990000"}

<html>
<head>

</head>
<body>
::: wrapper
::: {.box .a}
```{r hotspots_dengue_cosamaloapan}
# Step 1. extract the locality ####
loc <- rgeomex::extract_locality(cve_edo = "30", 
                                 locality = "Cosamaloapan")

# Step 2. Extract the hotspots ####
hotspots <- hotspotsdata::den_hotspots[loc, ]
mapview::mapview(hotspots,
                 zcol = "intensity_gi",
                 layer.name = "Intensidad",
                 label = FALSE,
                 color = "white",
                 lwd = 0.5, 
                 col.regions =  rcartocolor::carto_pal(n = max(hotspots$intensity_gi), 
                                                       name = "OrYel"))

```
:::

::: {.box .b}
```{r forest_plot_cosamaloapan, dpi = 300, fig.height= 5,fig.width = 7,fig.align = "center", out.height='100%', out.width = '100%',fig.show = "hold"}
 
# Logistic Regression
hotspots <- hotspots |>
    dplyr::mutate(DENV_2008_2010 = DENV_2008 + DENV_2009 + DENV_2010) |>
    dplyr::mutate(DENV_2011_2014 = DENV_2011 + DENV_2012 + DENV_2013 + DENV_2014) |>
    dplyr::mutate(DENV_2015_2017 = DENV_2015 +  DENV_2016 + DENV_2017) |>
    dplyr::mutate(DENV_2018_2019 = DENV_2018 +  DENV_2019) |>
    dplyr::mutate(DENV_2020_2022 = DENV_2020 +  DENV_2021 + DENV_2022) |>
    dplyr::mutate(DENV_2023_2024 = DENV_2023 +  DENV_2024) 


# Logistic Regression
glm.fit <- glm(hotspots_gi~DENV_2008_2010 + DENV_2011_2014 +
                   DENV_2015_2017 + DENV_2018_2019 +
                   DENV_2020_2022 + DENV_2023_2024,
               data = hotspots, 
               family = binomial)

result <- parameters::model_parameters(glm.fit, 
                                       exponentiate = FALSE)

plotly::ggplotly(plot(result) +
       ggplot2::theme(axis.text.y = ggplot2::element_text(size = 8),
                       axis.text.x = ggplot2::element_text(size = 8),
                       axis.title = ggplot2::element_text(size = 8),
                      plot.margin = ggplot2::unit(c(0,0,0,0), "cm")) +
        ggplot2::scale_y_discrete(labels = c("2008-2010",
                                             "2011-2014", 
                                             "2015-2017",
                                             "2018-2019",
                                             "2020-2022",
                                             "2023-2024")))
```
:::

::: {.box .c}
```{r power_law_plot_cosamaloapan,dpi = 300, warning=FALSE, fig.align = "center", out.width = '100%',out.height='100%',fig.show = "hold"}
# Step 7. make the function por calculate the cumulative ####
funcumsum <- function(x){
    x$cumulative_n <- cumsum(x$n_cases)
    x$perc_cumsum_n <- round((cumsum(x$n_cases)/sum(x$n_cases))*100, digits = 1)
    #x$cumulative_ha <- cumsum(x$ha)
    #x$perc_cumsum_ha <- round((cumsum(x$ha)/sum(x$ha))*100, digits = 1)
    x$id <- 1
    x$id_cumsum <- cumsum(x$id)
    x$id_perc_cum <- round((cumsum(x$id)/nrow(x))*100, digits = 1)
    x
}
# step 8.
data_pareto <- hotspots   |>
    # sf::st_drop_geometry()  |>
    # dplyr::mutate(n_cases = rowSums(dplyr::select(., dplyr::starts_with("DENV"))),
    #              loc = "locality")
    #dplyr::mutate(n_cases = rowSums(dplyr::across(DENV_2008:DENV_2021)),
    #              loc = "locality")  |>
    dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    
    dplyr::select(loc, n_cases, hotspots_gi)  |>
    dplyr::arrange(loc, desc(hotspots_gi), desc(n_cases))  |>
    dplyr::group_by(loc)  |>
    tidyr::nest()  |>
    dplyr::mutate(pareto_cases = purrr::map(data,
                                            funcumsum))  |>
    dplyr::select(-data)  |>
    tidyr::unnest(cols = c(pareto_cases))

# step 4. visualization of pareto rules 
plotly::ggplotly(denhotspots::power_law_plot(x = data_pareto) +
                  ggplot2::theme(axis.text.y = ggplot2::element_text(size = 8),
                                 axis.text.x = ggplot2::element_text(size = 8),
                       axis.title = ggplot2::element_text(size = 8),
                      plot.margin = ggplot2::unit(c(0,0,0,0), "cm")))  |> 
  plotly::layout(showlegend = FALSE)






```
:::

::: {.box .d}
```{r gauge_blocks_cosamaloapan,fig.align = "center", out.height='90%', out.width = '90%'}
y_hot <- hotspots |> dplyr::filter(hotspots_gi == 1)
centroid <- rgeomex::blocks_ine20_mx_centroid |>
  sf::st_as_sf(coords = c("x", "y"), crs = 4326)
b_loc <- centroid[hotspots, ]
b_hot <- b_loc[y_hot, ]
flexdashboard::gauge(round((nrow(b_hot)/nrow(b_loc))*100, digits = 1),
                     min = 0, max = 100, 
                     symbol = '%', 
                     label = "Manzanas",
                     flexdashboard::gaugeSectors(success = c(0, 30), 
                                                 warning = c(31, 50), 
                                                 danger = c(51, 100),
                                                 colors = c("#11BB33", #"#63C1A0", 
                                                            "#FC8427",
                                                            "#E01A59")))
```
:::

::: {.box .e}
```{r gauge_AGEB_cosamaloapan, fig.align = "center", out.height='90%', out.width = '90%'}

y <- hotspots  |>
    sf::st_drop_geometry() |>
     dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    dplyr::select(loc, n_cases, hotspots_gi) 
y_hot <- y |>dplyr::filter(hotspots_gi == 1)
  
flexdashboard::gauge(round((nrow(y_hot)/nrow(y))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "AGEBs",
      flexdashboard::gaugeSectors(success = c(0, 30), 
                                  warning = c(31, 50), 
                                  danger = c(51, 100),
                                  colors = c("#11BB33",
                                             "#FC8427",
                                             "#E01A59")))
```
:::

::: {.box .f}
```{r gauge_casos_cosamaloapan, out.height='90%', out.width = '90%', fig.align = "center"}

y <- hotspots  |>
    sf::st_drop_geometry() |>
      dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    dplyr::select(loc, n_cases, hotspots_gi) 
y_hot <- y |>dplyr::filter(hotspots_gi == 1)

flexdashboard::gauge(round((sum(y_hot$n_cases)/sum(y$n_cases))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "Casos de Dengue",
      flexdashboard::gaugeSectors(success = c(11, 100), 
                                  warning = c(6, 10), 
                                  danger = c(0, 5),
                                  colors = c("#11BB33", 
                                             "#FC8427",
                                             "#E01A59")))
```
:::
:::
</body>
</html>


### [**San 츼ndres Tuxtla**]{style="color:#990000"}

<html>
<head>

</head>
<body>
::: wrapper
::: {.box .a}
```{r hotspots_dengue_san_andres_tuxtla}
# Step 1. extract the locality ####
loc <- rgeomex::extract_locality(cve_edo = "30", 
                                 locality = "San Andres Tuxtla")

# Step 2. Extract the hotspots ####
hotspots <- hotspotsdata::den_hotspots[loc, ]
mapview::mapview(hotspots,
                 zcol = "intensity_gi",
                 layer.name = "Intensidad",
                 label = FALSE,
                 color = "white",
                 lwd = 0.5, 
                 col.regions =  rcartocolor::carto_pal(n = max(hotspots$intensity_gi), 
                                                       name = "OrYel"))

```
:::

::: {.box .b}
```{r forest_plot_san_andres_tuxtla, dpi = 300, fig.height= 5,fig.width = 7,fig.align = "center", out.height='100%', out.width = '100%',fig.show = "hold"}
 
# Logistic Regression
hotspots <- hotspots |>
    dplyr::mutate(DENV_2008_2010 = DENV_2008 + DENV_2009 + DENV_2010) |>
    dplyr::mutate(DENV_2011_2014 = DENV_2011 + DENV_2012 + DENV_2013 + DENV_2014) |>
    dplyr::mutate(DENV_2015_2017 = DENV_2015 +  DENV_2016 + DENV_2017) |>
    dplyr::mutate(DENV_2018_2019 = DENV_2018 +  DENV_2019) |>
    dplyr::mutate(DENV_2020_2022 = DENV_2020 +  DENV_2021 + DENV_2022) |>
    dplyr::mutate(DENV_2023_2024 = DENV_2023 +  DENV_2024) 


# Logistic Regression
glm.fit <- glm(hotspots_gi~DENV_2008_2010 + DENV_2011_2014 +
                   DENV_2015_2017 + DENV_2018_2019 +
                   DENV_2020_2022 + DENV_2023_2024,
               data = hotspots, 
               family = binomial)

result <- parameters::model_parameters(glm.fit, 
                                       exponentiate = FALSE)

plotly::ggplotly(plot(result) +
       ggplot2::theme(axis.text.y = ggplot2::element_text(size = 8),
                       axis.text.x = ggplot2::element_text(size = 8),
                       axis.title = ggplot2::element_text(size = 8),
                      plot.margin = ggplot2::unit(c(0,0,0,0), "cm")) +
        ggplot2::scale_y_discrete(labels = c("2008-2010",
                                             "2011-2014", 
                                             "2015-2017",
                                             "2018-2019",
                                             "2020-2022",
                                             "2023-2024")))
```
:::

::: {.box .c}
```{r power_law_plot_san_andres_tuxtla,dpi = 300, warning=FALSE, fig.align = "center", out.width = '100%',out.height='100%',fig.show = "hold"}
# Step 7. make the function por calculate the cumulative ####
funcumsum <- function(x){
    x$cumulative_n <- cumsum(x$n_cases)
    x$perc_cumsum_n <- round((cumsum(x$n_cases)/sum(x$n_cases))*100, digits = 1)
    #x$cumulative_ha <- cumsum(x$ha)
    #x$perc_cumsum_ha <- round((cumsum(x$ha)/sum(x$ha))*100, digits = 1)
    x$id <- 1
    x$id_cumsum <- cumsum(x$id)
    x$id_perc_cum <- round((cumsum(x$id)/nrow(x))*100, digits = 1)
    x
}
# step 8.
data_pareto <- hotspots   |>
    # sf::st_drop_geometry()  |>
    # dplyr::mutate(n_cases = rowSums(dplyr::select(., dplyr::starts_with("DENV"))),
    #              loc = "locality")
    #dplyr::mutate(n_cases = rowSums(dplyr::across(DENV_2008:DENV_2021)),
    #              loc = "locality")  |>
    dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    
    dplyr::select(loc, n_cases, hotspots_gi)  |>
    dplyr::arrange(loc, desc(hotspots_gi), desc(n_cases))  |>
    dplyr::group_by(loc)  |>
    tidyr::nest()  |>
    dplyr::mutate(pareto_cases = purrr::map(data,
                                            funcumsum))  |>
    dplyr::select(-data)  |>
    tidyr::unnest(cols = c(pareto_cases))

# step 4. visualization of pareto rules 
plotly::ggplotly(denhotspots::power_law_plot(x = data_pareto) +
                  ggplot2::theme(axis.text.y = ggplot2::element_text(size = 8),
                                 axis.text.x = ggplot2::element_text(size = 8),
                       axis.title = ggplot2::element_text(size = 8),
                      plot.margin = ggplot2::unit(c(0,0,0,0), "cm")))  |> 
  plotly::layout(showlegend = FALSE)






```
:::

::: {.box .d}
```{r gauge_blocks_san_andres_tuxtla,fig.align = "center", out.height='90%', out.width = '90%'}
y_hot <- hotspots |> dplyr::filter(hotspots_gi == 1)
centroid <- rgeomex::blocks_ine20_mx_centroid |>
  sf::st_as_sf(coords = c("x", "y"), crs = 4326)
b_loc <- centroid[hotspots, ]
b_hot <- b_loc[y_hot, ]
flexdashboard::gauge(round((nrow(b_hot)/nrow(b_loc))*100, digits = 1),
                     min = 0, max = 100, 
                     symbol = '%', 
                     label = "Manzanas",
                     flexdashboard::gaugeSectors(success = c(0, 30), 
                                                 warning = c(31, 50), 
                                                 danger = c(51, 100),
                                                 colors = c("#11BB33", #"#63C1A0", 
                                                            "#FC8427",
                                                            "#E01A59")))
```
:::

::: {.box .e}
```{r gauge_AGEB_san_andres_tuxtla, fig.align = "center", out.height='90%', out.width = '90%'}

y <- hotspots  |>
    sf::st_drop_geometry() |>
     dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    dplyr::select(loc, n_cases, hotspots_gi) 
y_hot <- y |>dplyr::filter(hotspots_gi == 1)
  
flexdashboard::gauge(round((nrow(y_hot)/nrow(y))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "AGEBs",
      flexdashboard::gaugeSectors(success = c(0, 30), 
                                  warning = c(31, 50), 
                                  danger = c(51, 100),
                                  colors = c("#11BB33",
                                             "#FC8427",
                                             "#E01A59")))
```
:::

::: {.box .f}
```{r gauge_casos_san_andres_tuxtla, out.height='90%', out.width = '90%', fig.align = "center"}

y <- hotspots  |>
    sf::st_drop_geometry() |>
      dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    dplyr::select(loc, n_cases, hotspots_gi) 
y_hot <- y |>dplyr::filter(hotspots_gi == 1)

flexdashboard::gauge(round((sum(y_hot$n_cases)/sum(y$n_cases))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "Casos de Dengue",
      flexdashboard::gaugeSectors(success = c(11, 100), 
                                  warning = c(6, 10), 
                                  danger = c(0, 5),
                                  colors = c("#11BB33", 
                                             "#FC8427",
                                             "#E01A59")))
```
:::
:::
</body>
</html>



### [**Coatzacoalcos**]{style="color:#990000"}

<html>
<head>

</head>
<body>
::: wrapper
::: {.box .a}
```{r hotspots_dengue_coatzacoalcos}
# Step 1. extract the locality ####
loc <- rgeomex::extract_locality(cve_edo = "30", 
                                 locality = "Coatzacoalcos")

# Step 2. Extract the hotspots ####
hotspots <- hotspotsdata::den_hotspots[loc, ]
mapview::mapview(hotspots,
                 zcol = "intensity_gi",
                 layer.name = "Intensidad",
                 label = FALSE,
                 color = "white",
                 lwd = 0.5, 
                 col.regions =  rcartocolor::carto_pal(n = max(hotspots$intensity_gi), 
                                                       name = "OrYel"))

```
:::

::: {.box .b}
```{r forest_plot_coatzacoalcos, dpi = 300, fig.height= 5,fig.width = 7,fig.align = "center", out.height='100%', out.width = '100%',fig.show = "hold"}
 
# Logistic Regression
hotspots <- hotspots |>
    dplyr::mutate(DENV_2008_2010 = DENV_2008 + DENV_2009 + DENV_2010) |>
    dplyr::mutate(DENV_2011_2014 = DENV_2011 + DENV_2012 + DENV_2013 + DENV_2014) |>
    dplyr::mutate(DENV_2015_2017 = DENV_2015 +  DENV_2016 + DENV_2017) |>
    dplyr::mutate(DENV_2018_2019 = DENV_2018 +  DENV_2019) |>
    dplyr::mutate(DENV_2020_2022 = DENV_2020 +  DENV_2021 + DENV_2022) |>
    dplyr::mutate(DENV_2023_2024 = DENV_2023 +  DENV_2024) 


# Logistic Regression
glm.fit <- glm(hotspots_gi~DENV_2008_2010 + DENV_2011_2014 +
                   DENV_2015_2017 + DENV_2018_2019 +
                   DENV_2020_2022 + DENV_2023_2024,
               data = hotspots, 
               family = binomial)

result <- parameters::model_parameters(glm.fit, 
                                       exponentiate = FALSE)

plotly::ggplotly(plot(result) +
       ggplot2::theme(axis.text.y = ggplot2::element_text(size = 8),
                       axis.text.x = ggplot2::element_text(size = 8),
                       axis.title = ggplot2::element_text(size = 8),
                      plot.margin = ggplot2::unit(c(0,0,0,0), "cm")) +
        ggplot2::scale_y_discrete(labels = c("2008-2010",
                                             "2011-2014", 
                                             "2015-2017",
                                             "2018-2019",
                                             "2020-2022",
                                             "2023-2024")))
```
:::

::: {.box .c}
```{r power_law_plot_coatzacoalcos,dpi = 300, warning=FALSE, fig.align = "center", out.width = '100%',out.height='100%',fig.show = "hold"}
# Step 7. make the function por calculate the cumulative ####
funcumsum <- function(x){
    x$cumulative_n <- cumsum(x$n_cases)
    x$perc_cumsum_n <- round((cumsum(x$n_cases)/sum(x$n_cases))*100, digits = 1)
    #x$cumulative_ha <- cumsum(x$ha)
    #x$perc_cumsum_ha <- round((cumsum(x$ha)/sum(x$ha))*100, digits = 1)
    x$id <- 1
    x$id_cumsum <- cumsum(x$id)
    x$id_perc_cum <- round((cumsum(x$id)/nrow(x))*100, digits = 1)
    x
}
# step 8.
data_pareto <- hotspots   |>
    # sf::st_drop_geometry()  |>
    # dplyr::mutate(n_cases = rowSums(dplyr::select(., dplyr::starts_with("DENV"))),
    #              loc = "locality")
    #dplyr::mutate(n_cases = rowSums(dplyr::across(DENV_2008:DENV_2021)),
    #              loc = "locality")  |>
    dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    
    dplyr::select(loc, n_cases, hotspots_gi)  |>
    dplyr::arrange(loc, desc(hotspots_gi), desc(n_cases))  |>
    dplyr::group_by(loc)  |>
    tidyr::nest()  |>
    dplyr::mutate(pareto_cases = purrr::map(data,
                                            funcumsum))  |>
    dplyr::select(-data)  |>
    tidyr::unnest(cols = c(pareto_cases))

# step 4. visualization of pareto rules 
plotly::ggplotly(denhotspots::power_law_plot(x = data_pareto) +
                  ggplot2::theme(axis.text.y = ggplot2::element_text(size = 8),
                                 axis.text.x = ggplot2::element_text(size = 8),
                       axis.title = ggplot2::element_text(size = 8),
                      plot.margin = ggplot2::unit(c(0,0,0,0), "cm")))  |> 
  plotly::layout(showlegend = FALSE)






```
:::

::: {.box .d}
```{r gauge_blocks_coatzacoalcos,fig.align = "center", out.height='90%', out.width = '90%'}
y_hot <- hotspots |> dplyr::filter(hotspots_gi == 1)
centroid <- rgeomex::blocks_ine20_mx_centroid |>
  sf::st_as_sf(coords = c("x", "y"), crs = 4326)
b_loc <- centroid[hotspots, ]
b_hot <- b_loc[y_hot, ]
flexdashboard::gauge(round((nrow(b_hot)/nrow(b_loc))*100, digits = 1),
                     min = 0, max = 100, 
                     symbol = '%', 
                     label = "Manzanas",
                     flexdashboard::gaugeSectors(success = c(0, 30), 
                                                 warning = c(31, 50), 
                                                 danger = c(51, 100),
                                                 colors = c("#11BB33", #"#63C1A0", 
                                                            "#FC8427",
                                                            "#E01A59")))
```
:::

::: {.box .e}
```{r gauge_AGEB_coatzacoalcos, fig.align = "center", out.height='90%', out.width = '90%'}

y <- hotspots  |>
    sf::st_drop_geometry() |>
     dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    dplyr::select(loc, n_cases, hotspots_gi) 
y_hot <- y |>dplyr::filter(hotspots_gi == 1)
  
flexdashboard::gauge(round((nrow(y_hot)/nrow(y))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "AGEBs",
      flexdashboard::gaugeSectors(success = c(0, 30), 
                                  warning = c(31, 50), 
                                  danger = c(51, 100),
                                  colors = c("#11BB33",
                                             "#FC8427",
                                             "#E01A59")))
```
:::

::: {.box .f}
```{r gauge_casos_coatzacoalcos, out.height='90%', out.width = '90%', fig.align = "center"}

y <- hotspots  |>
    sf::st_drop_geometry() |>
      dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    dplyr::select(loc, n_cases, hotspots_gi) 
y_hot <- y |>dplyr::filter(hotspots_gi == 1)

flexdashboard::gauge(round((sum(y_hot$n_cases)/sum(y$n_cases))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "Casos de Dengue",
      flexdashboard::gaugeSectors(success = c(11, 100), 
                                  warning = c(6, 10), 
                                  danger = c(0, 5),
                                  colors = c("#11BB33", 
                                             "#FC8427",
                                             "#E01A59")))
```
:::
:::
</body>
</html>



### [**Minatitl치n**]{style="color:#990000"}

<html>
<head>

</head>
<body>
::: wrapper
::: {.box .a}
```{r hotspots_dengue_mina}
# Step 1. extract the locality ####
loc <- rgeomex::extract_locality(cve_edo = "30", 
                                 locality = "Minatitl치n")

# Step 2. Extract the hotspots ####
hotspots <- hotspotsdata::den_hotspots[loc, ]
mapview::mapview(hotspots,
                 zcol = "intensity_gi",
                 layer.name = "Intensidad",
                 label = FALSE,
                 color = "white",
                 lwd = 0.5, 
                 col.regions =  rcartocolor::carto_pal(n = max(hotspots$intensity_gi), 
                                                       name = "OrYel"))

```
:::

::: {.box .b}
```{r forest_plot_mina, dpi = 300, fig.height= 5,fig.width = 7,fig.align = "center", out.height='100%', out.width = '100%',fig.show = "hold"}
 
# Logistic Regression
hotspots <- hotspots |>
    dplyr::mutate(DENV_2008_2010 = DENV_2008 + DENV_2009 + DENV_2010) |>
    dplyr::mutate(DENV_2011_2014 = DENV_2011 + DENV_2012 + DENV_2013 + DENV_2014) |>
    dplyr::mutate(DENV_2015_2017 = DENV_2015 +  DENV_2016 + DENV_2017) |>
    dplyr::mutate(DENV_2018_2019 = DENV_2018 +  DENV_2019) |>
    dplyr::mutate(DENV_2020_2022 = DENV_2020 +  DENV_2021 + DENV_2022) |>
    dplyr::mutate(DENV_2023_2024 = DENV_2023 +  DENV_2024) 


# Logistic Regression
glm.fit <- glm(hotspots_gi~DENV_2008_2010 + DENV_2011_2014 +
                   DENV_2015_2017 + DENV_2018_2019 +
                   DENV_2020_2022 + DENV_2023_2024,
               data = hotspots, 
               family = binomial)

result <- parameters::model_parameters(glm.fit, 
                                       exponentiate = FALSE)

plotly::ggplotly(plot(result) +
       ggplot2::theme(axis.text.y = ggplot2::element_text(size = 8),
                       axis.text.x = ggplot2::element_text(size = 8),
                       axis.title = ggplot2::element_text(size = 8),
                      plot.margin = ggplot2::unit(c(0,0,0,0), "cm")) +
        ggplot2::scale_y_discrete(labels = c("2008-2010",
                                             "2011-2014", 
                                             "2015-2017",
                                             "2018-2019",
                                             "2020-2022",
                                             "2023-2024")))
```
:::

::: {.box .c}
```{r power_law_plot_mina,dpi = 300, warning=FALSE, fig.align = "center", out.width = '100%',out.height='100%',fig.show = "hold"}
# Step 7. make the function por calculate the cumulative ####
funcumsum <- function(x){
    x$cumulative_n <- cumsum(x$n_cases)
    x$perc_cumsum_n <- round((cumsum(x$n_cases)/sum(x$n_cases))*100, digits = 1)
    #x$cumulative_ha <- cumsum(x$ha)
    #x$perc_cumsum_ha <- round((cumsum(x$ha)/sum(x$ha))*100, digits = 1)
    x$id <- 1
    x$id_cumsum <- cumsum(x$id)
    x$id_perc_cum <- round((cumsum(x$id)/nrow(x))*100, digits = 1)
    x
}
# step 8.
data_pareto <- hotspots   |>
    # sf::st_drop_geometry()  |>
    # dplyr::mutate(n_cases = rowSums(dplyr::select(., dplyr::starts_with("DENV"))),
    #              loc = "locality")
    #dplyr::mutate(n_cases = rowSums(dplyr::across(DENV_2008:DENV_2021)),
    #              loc = "locality")  |>
    dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    
    dplyr::select(loc, n_cases, hotspots_gi)  |>
    dplyr::arrange(loc, desc(hotspots_gi), desc(n_cases))  |>
    dplyr::group_by(loc)  |>
    tidyr::nest()  |>
    dplyr::mutate(pareto_cases = purrr::map(data,
                                            funcumsum))  |>
    dplyr::select(-data)  |>
    tidyr::unnest(cols = c(pareto_cases))

# step 4. visualization of pareto rules 
plotly::ggplotly(denhotspots::power_law_plot(x = data_pareto) +
                  ggplot2::theme(axis.text.y = ggplot2::element_text(size = 8),
                                 axis.text.x = ggplot2::element_text(size = 8),
                       axis.title = ggplot2::element_text(size = 8),
                      plot.margin = ggplot2::unit(c(0,0,0,0), "cm")))  |> 
  plotly::layout(showlegend = FALSE)






```
:::

::: {.box .d}
```{r gauge_blocks_mina,fig.align = "center", out.height='90%', out.width = '90%'}
y_hot <- hotspots |> dplyr::filter(hotspots_gi == 1)
centroid <- rgeomex::blocks_ine20_mx_centroid |>
  sf::st_as_sf(coords = c("x", "y"), crs = 4326)
b_loc <- centroid[hotspots, ]
b_hot <- b_loc[y_hot, ]
flexdashboard::gauge(round((nrow(b_hot)/nrow(b_loc))*100, digits = 1),
                     min = 0, max = 100, 
                     symbol = '%', 
                     label = "Manzanas",
                     flexdashboard::gaugeSectors(success = c(0, 30), 
                                                 warning = c(31, 50), 
                                                 danger = c(51, 100),
                                                 colors = c("#11BB33", #"#63C1A0", 
                                                            "#FC8427",
                                                            "#E01A59")))
```
:::

::: {.box .e}
```{r gauge_AGEB_mina, fig.align = "center", out.height='90%', out.width = '90%'}

y <- hotspots  |>
    sf::st_drop_geometry() |>
     dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    dplyr::select(loc, n_cases, hotspots_gi) 
y_hot <- y |>dplyr::filter(hotspots_gi == 1)
  
flexdashboard::gauge(round((nrow(y_hot)/nrow(y))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "AGEBs",
      flexdashboard::gaugeSectors(success = c(0, 30), 
                                  warning = c(31, 50), 
                                  danger = c(51, 100),
                                  colors = c("#11BB33",
                                             "#FC8427",
                                             "#E01A59")))
```
:::

::: {.box .f}
```{r gauge_casos_mina, out.height='90%', out.width = '90%', fig.align = "center"}

y <- hotspots  |>
    sf::st_drop_geometry() |>
      dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    dplyr::select(loc, n_cases, hotspots_gi) 
y_hot <- y |>dplyr::filter(hotspots_gi == 1)

flexdashboard::gauge(round((sum(y_hot$n_cases)/sum(y$n_cases))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "Casos de Dengue",
      flexdashboard::gaugeSectors(success = c(11, 100), 
                                  warning = c(6, 10), 
                                  danger = c(0, 5),
                                  colors = c("#11BB33", 
                                             "#FC8427",
                                             "#E01A59")))
```
:::
:::
</body>
</html>


:::


# [**Hotspots del vector**]{style="font-size:2pt"}
 
::: panel-tabset


### [**Tuxpan**]{style="color:#990000"}

```{r vector_hotspots_tuxpan, dpi = 300, warning=FALSE, message=FALSE}
deneggs::map_eggs_hotspots(betas = denmex::eggs_betas_30_veracruz,
                           locality = "Tuxpan de Rodriguez Cano",
                           cve_edo = "30",
                           palette = rcartocolor::carto_pal,
                           name = "SunsetDark",
                           static_map = FALSE)
```


### [**Poza Rica**]{style="color:#990000"}

```{r vector_hotspots_poza_rica, dpi = 300, warning=FALSE, message=FALSE}
deneggs::map_eggs_hotspots(betas = denmex::eggs_betas_30_veracruz,
                           locality = "Poza Rica Hidalgo",
                           cve_edo = "30",
                           palette = rcartocolor::carto_pal,
                           name = "SunsetDark",
                           static_map = FALSE)
```


### [**Papantla**]{style="color:#990000"}

```{r vector_hotspots_papantla, dpi = 300, warning=FALSE, message=FALSE}
deneggs::map_eggs_hotspots(betas = denmex::eggs_betas_30_veracruz,
                           locality = "Papantla de Olearte",
                           cve_edo = "30",
                           palette = rcartocolor::carto_pal,
                           name = "SunsetDark",
                           static_map = FALSE)
```

### [**Mart칤nez de la Torre**]{style="color:#990000"}

```{r vector_hotspots_martinez, dpi = 300, warning=FALSE, message=FALSE}
deneggs::map_eggs_hotspots(betas = denmex::eggs_betas_30_veracruz,
                           locality = "Martinez de la Torre",
                           cve_edo = "30",
                           palette = rcartocolor::carto_pal,
                           name = "SunsetDark",
                           static_map = FALSE)
```

### [**Xalapa**]{style="color:#990000"}

```{r vector_hotspots_xalapa, dpi = 300, warning=FALSE, message=FALSE}
deneggs::map_eggs_hotspots(betas = denmex::eggs_betas_30_veracruz,
                           locality = "Xalapa de Ordo침ez",
                           cve_edo = "30",
                           palette = rcartocolor::carto_pal,
                           name = "SunsetDark",
                           static_map = FALSE)
```


### [**C칩rdoba**]{style="color:#990000"}

```{r vector_hotspots_cordoba, dpi = 300, warning=FALSE, message=FALSE}
deneggs::map_eggs_hotspots(betas = denmex::eggs_betas_30_veracruz,
                           locality = "C치rdoba",
                           cve_edo = "30",
                           palette = rcartocolor::carto_pal,
                           name = "SunsetDark",
                           static_map = FALSE)
```

### [**Orizaba**]{style="color:#990000"}

```{r vector_hotspots_orizaba, dpi = 300, warning=FALSE, message=FALSE}
deneggs::map_eggs_hotspots(betas = denmex::eggs_betas_30_veracruz,
                           locality = "Orizaba",
                           cve_edo = "30",
                           palette = rcartocolor::carto_pal,
                           name = "SunsetDark",
                           static_map = FALSE)
```

### [**Veracruz**]{style="color:#990000"}

```{r vector_hotspots_veracruz, dpi = 300, warning=FALSE, message=FALSE}
deneggs::map_eggs_hotspots(betas = denmex::eggs_betas_30_veracruz,
                           locality = c("Veracruz", "Bocal del Rio"),
                           cve_edo = "30",
                           palette = rcartocolor::carto_pal,
                           name = "SunsetDark",
                           static_map = FALSE)
```


### [**San Andres Tuxtla**]{style="color:#990000"}

```{r vector_hotspots_san_andres, dpi = 300, warning=FALSE, message=FALSE}
deneggs::map_eggs_hotspots(betas = denmex::eggs_betas_30_veracruz,
                           locality = "San Andres Tuxtla",
                           cve_edo = "30",
                           palette = rcartocolor::carto_pal,
                           name = "SunsetDark",
                           static_map = FALSE)
```


### [**Cosamoloapan**]{style="color:#990000"}

```{r vector_hotspots_cosamaloapan, dpi = 300, warning=FALSE, message=FALSE}
deneggs::map_eggs_hotspots(betas = denmex::eggs_betas_30_veracruz,
                           locality = "Cosamaloapan",
                           cve_edo = "30",
                           palette = rcartocolor::carto_pal,
                           name = "SunsetDark",
                           static_map = FALSE)
```

### [**Coatzacoalcos**]{style="color:#990000"}

```{r vector_hotspots_coatza, dpi = 300, warning=FALSE, message=FALSE}
deneggs::map_eggs_hotspots(betas = denmex::eggs_betas_30_veracruz,
                           locality = "Coatzacoalcos",
                           cve_edo = "30",
                           palette = rcartocolor::carto_pal,
                           name = "SunsetDark",
                           static_map = FALSE)
```

### [**Minatitlan**]{style="color:#990000"}

```{r vector_hotspots_mina, dpi = 300, warning=FALSE, message=FALSE}
deneggs::map_eggs_hotspots(betas = denmex::eggs_betas_30_veracruz,
                           locality = "Minatitlan",
                           cve_edo = "30",
                           palette = rcartocolor::carto_pal,
                           name = "SunsetDark",
                           static_map = FALSE)
```


:::



# [**Escenarios Epidemiol칩gicos**]{style="font-size:2pt"}
 
::: panel-tabset


### [**Tuxpan**]{style="color:#990000"}

```{r risk_ageb_tuxpan}
# Step 1. calculate the risk ####
denhotspots::risk_ageb(betas = denmex::eggs_betas_30_veracruz,
                       hotspots = denmex::den_hotspots,
                       intensity_perc = 25,
                       locality = "Tuxpan de Rodriguez Cano",
                       cve_edo = "30") |>
  denhotspots::map_risk(staticmap = FALSE)

```


### [**Poza Rica**]{style="color:#990000"}

```{r risk_ageb_poza_rica}
# Step 1. calculate the risk ####
denhotspots::risk_ageb(betas = denmex::eggs_betas_30_veracruz,
                       hotspots = denmex::den_hotspots,
                       intensity_perc = 25,
                       locality = "Poza Rica de Hidalgo",
                       cve_edo = "30") |>
  denhotspots::map_risk(staticmap = FALSE)

```


### [**Papantla**]{style="color:#990000"}

```{r risk_ageb_papantla}
# Step 1. calculate the risk ####
denhotspots::risk_ageb(betas = denmex::eggs_betas_30_veracruz,
                       hotspots = denmex::den_hotspots,
                       intensity_perc = 25,
                       locality = "Papantla de Olearte",
                       cve_edo = "30") |>
  denhotspots::map_risk(staticmap = FALSE)

```


### [**Mart칤nez de la Torre**]{style="color:#990000"}

```{r risk_ageb_martinez}
# Step 1. calculate the risk ####
denhotspots::risk_ageb(betas = denmex::eggs_betas_30_veracruz,
                       hotspots = denmex::den_hotspots,
                       intensity_perc = 25,
                       locality = "Mart칤nez de la Torre",
                       cve_edo = "30") |>
  denhotspots::map_risk(staticmap = FALSE)

```

### [**Xalapa**]{style="color:#990000"}

```{r risk_ageb_xalapa}
# Step 1. calculate the risk ####
denhotspots::risk_ageb(betas = denmex::eggs_betas_30_veracruz,
                       hotspots = denmex::den_hotspots,
                       intensity_perc = 25,
                       locality = "Xalapa de Ordo침ez",
                       cve_edo = "30") |>
  denhotspots::map_risk(staticmap = FALSE)

```

### [**C칩rdoba**]{style="color:#990000"}

```{r risk_ageb_cordoba}
# Step 1. calculate the risk ####
denhotspots::risk_ageb(betas = denmex::eggs_betas_30_veracruz,
                       hotspots = denmex::den_hotspots,
                       intensity_perc = 25,
                       locality = "C치rdoba",
                       cve_edo = "30") |>
  denhotspots::map_risk(staticmap = FALSE)

```

### [**Orizaba**]{style="color:#990000"}

```{r risk_ageb_orizaba}
# Step 1. calculate the risk ####
denhotspots::risk_ageb(betas = denmex::eggs_betas_30_veracruz,
                       hotspots = denmex::den_hotspots,
                       intensity_perc = 25,
                       locality = "Orizaba",
                       cve_edo = "30") |>
  denhotspots::map_risk(staticmap = FALSE)

```


### [**Veracruz**]{style="color:#990000"}

```{r risk_ageb_veracruz}
# Step 1. calculate the risk ####
denhotspots::risk_ageb(betas = denmex::eggs_betas_30_veracruz,
                       hotspots = denmex::den_hotspots,
                       intensity_perc = 25,
                       locality = c("Veracruz", "Boca del R칤o"),
                       cve_edo = "30") |>
  denhotspots::map_risk(staticmap = FALSE)

```


### [**Cosamaloapan**]{style="color:#990000"}

```{r risk_ageb_cosa}
# Step 1. calculate the risk ####
denhotspots::risk_ageb(betas = denmex::eggs_betas_30_veracruz,
                       hotspots = denmex::den_hotspots,
                       intensity_perc = 25,
                       locality = "Cosamaloapan",
                       cve_edo = "30") |>
  denhotspots::map_risk(staticmap = FALSE)

```


### [**San 츼ndres Tuxtla**]{style="color:#990000"}

```{r risk_ageb_san_andres}
# Step 1. calculate the risk ####
denhotspots::risk_ageb(betas = denmex::eggs_betas_30_veracruz,
                       hotspots = denmex::den_hotspots,
                       intensity_perc = 25,
                       locality = "San Andres Tuxtal",
                       cve_edo = "30") |>
  denhotspots::map_risk(staticmap = FALSE)

```


### [**Coatzacoalcos**]{style="color:#990000"}

```{r risk_ageb_coatza}
# Step 1. calculate the risk ####
denhotspots::risk_ageb(betas = denmex::eggs_betas_30_veracruz,
                       hotspots = denmex::den_hotspots,
                       intensity_perc = 25,
                       locality = "Coatzacoalcos",
                       cve_edo = "30") |>
  denhotspots::map_risk(staticmap = FALSE)

```

### [**Minatitl치n**]{style="color:#990000"}

```{r risk_ageb_mina}
# Step 1. calculate the risk ####
denhotspots::risk_ageb(betas = denmex::eggs_betas_30_veracruz,
                       hotspots = denmex::den_hotspots,
                       intensity_perc = 25,
                       locality = "Minatitlan",
                       cve_edo = "30") |>
  denhotspots::map_risk(staticmap = FALSE)

```

:::



